\chapter{Results}
\section{Achievements}
The main goal of this project described below has been met. This goal contained a lot of sub-goals which ultimately dwell down to one thing: converting OSM data into the NeTEx format.\\
\newline
Integrating OpenStreetMap with Public Transport Network Format "NeTEx" using the JOSM editor:
\begin{itemize}
	\item{Create a JOSM plugin in Java for converting OSM data into NeTEx.}
	\begin{itemize}
		\item{Create a JOSM friendly plugin.}
		\item{Convert and export the loaded OSM data of JOSM into a single .XML file using the generated NeTEx Java model.}
		\item{Fix data inconsistency problems by identifying and saving missing tags/information}
		\item{Log the warning messages created while converting the data in the JOSM map layer relative elements}
		\item{Have the plugin deployed in a single \textit{.jar} file.}
	\end{itemize}
	\item{Translate the NeTEx XML schema into a Java model.}
	\item{Publish the plugin in the official JOSM plugins repository.}
\end{itemize}
\newpage
\section{Reflection}
I have never used OpenStreetMap before, let alone JOSM. This project made me learn a lot of key factors that drive OSM and make OSM such a successful project for the community. It also improved my ability to work in an open-source project and know the approaches that are used by developers when developing open-source projects.\\
\newline
I wasn't very informed about transport data either and never heard of NeTEx before either, so a combination of OSM and NeTEx was very beneficial for me. It is also the first time I have created something that is similar to converting data of a format into a completely different format. The process was a tough challenge but also a very rewarding one.\\
\newline
I have had a lot of experience with working with Java before, but not that much experience of coding in open-source projects where you have to code by following "protocol". I had to do a lot of research within the code, but after a while, I understood how the whole thing worked and then after that, everything in the code made sense and was straight-forward to reach in the code.\\
\newline
I have also never worked with an XML binding framework either and it was wonderful to see how such things are configured and implemented, without such frameworks, this would be impossible! A lot of technologies and approaches used here were a new experience for me and even though it was overwhelming sometimes, it was definitely worth it!